Results

### 2023-03-31 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
rephrasing of some sentences

#### Subjective arousal and physiological responding <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effect of valence on arousal and facial EMG." -->

@@

#### Subjective effort of ER strategies

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
Post-hoc test showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

The cognitive effort expended also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
Here, `r round((54/119)*100, digits = 1)`% stated that they chose the strategy that was easiest for them to implement.
`r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found in Table XX in [supplementary material](#SupplementReasonChoice).

>>>>

#### Subjective arousal and physiological responding <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effect of valence and emotion regulation on arousal and facial EMG." -->

@@

#### Subjective effort of ER strategies <!-- ich würde empfehlen, die selben Überschriften wie in 2.5 Analysis Plan zu nehmen, das wäre für diese Ergebnisse "Effects of emotion regulation on effort" -->

To investigate whether ER strategies require cognitive effort, we conducted an rmANOVA comparing the subjective effort ratings of four strategies (active viewing, distraction, distancing, suppression).
We found a significant effect of strategy (`r papaja::apa_print(SubjEffort_aov)$full_result`, `r papaja::apa_print(SubjEffort_BF)$statistic`; see figure\ \@ref(fig:FigSubjEffort)).
Post-hoc tests showed significantly higher subjective effort for distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X3distraction`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "3_distraction"],progress = FALSE, paired = TRUE))$statistic`), distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X4distancing`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "4_distancing"],progress = FALSE, paired = TRUE))$statistic`), and suppression (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X2viewneg_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "2_view_neg"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) compared to active viewing. 
Moreover, we found significantly lower effort during suppression compared with distraction (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X3distraction_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "3_distraction"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`) and distancing (`r papaja::apa_print(pairs(SubjEffort_emm))$statistic$X4distancing_X5suppression`, `r papaja::apa_print(BayesFactor::ttestBF(x = Ratings_reg$effort[Ratings_reg$block == "4_distancing"], y = Ratings_reg$effort[Ratings_reg$block == "5_suppression"],progress = FALSE, paired = TRUE))$statistic`).

@@

Cognitive effort also played the most important role in the subsequent choice decision, which resembled previous findings of our group[@Scheffel2021]. 
`r round((54/119)*100, digits = 1)`% of the participants stated that they chose the strategy that was easiest for them to implement.
`r round((29/119)*100, digits = 1)`% stated they chose the strategy that was most effective and `r round((14/119)*100, digits = 1)`% stated their chosen strategy was the easiest and most effective.
A more detailed list of all reasons can be found in Table XX <!-- Nummer noch ergänzen --> in [supplementary material](#SupplementReasonChoice).
